---
title: "R Notebook"
output: html_notebook
---

## PBMC H3K4me3 H3K27me3 Export Files

### Input Files

- `./tmp/ArchRProject_PBMCs_Combined_Beds_H3K27me3_Doublets_Removed_021126`
- `./tmp/ArchRProject_PBMCs_Combined_Beds_H3K4me3_Doublets_Removed_021126`

### Output Files And Directories

- `proj_K27me3_barcodes_NewClusters.tsv`
- `proj_K4me3_barcodes_NewClusters.tsv`
- `./tmp/Export_K27me3_PBMCs_Combined_Beds_Harmony_021126/`
- `./tmp/Export_K27me3_PBMCs_Combined_Beds_Harmony_021126/svd.csv`
- `./tmp/Export_K27me3_PBMCs_Combined_Beds_Harmony_021126/umap_harmony.csv`
- `./tmp/Export_K27me3_PBMCs_Combined_Beds_Harmony_021126/cell_metadata.csv`
- `./tmp/Export_K27me3_PBMCs_Combined_Beds_Harmony_021126/gene_scores/`
- `./tmp/Export_K27me3_PBMCs_Combined_Beds_Harmony_021126/gene_scores/scores.mtx`
- `./tmp/Export_K27me3_PBMCs_Combined_Beds_Harmony_021126/gene_scores/cells.csv`
- `./tmp/Export_K27me3_PBMCs_Combined_Beds_Harmony_021126/gene_scores/genes.csv`
- `./tmp/Export_K4me3_PBMCs_Combined_Beds_Harmony_021126/`
- `./tmp/Export_K4me3_PBMCs_Combined_Beds_Harmony_021126/svd.csv`
- `./tmp/Export_K4me3_PBMCs_Combined_Beds_Harmony_021126/umap_harmony.csv`
- `./tmp/Export_K4me3_PBMCs_Combined_Beds_Harmony_021126/cell_metadata.csv`
- `./tmp/Export_K4me3_PBMCs_Combined_Beds_Harmony_021126/gene_scores/`
- `./tmp/Export_K4me3_PBMCs_Combined_Beds_Harmony_021126/gene_scores/scores.mtx`
- `./tmp/Export_K4me3_PBMCs_Combined_Beds_Harmony_021126/gene_scores/cells.csv`
- `./tmp/Export_K4me3_PBMCs_Combined_Beds_Harmony_021126/gene_scores/genes.csv`


```{r}
Sys.unsetenv("DISPLAY")

suppressPackageStartupMessages({
    library(ArchR)
    library(parallel)
    library(rtracklayer)
    library(repr)
    library(dplyr)
    library(plyr)
    library(Seurat)
    library(ggplot2)
    library(GenomicRanges)
    library(rtracklayer)
})
set.seed(1)

# Set default plot size
options(repr.plot.width = 10, repr.plot.height = 10)
```


```{r}
addArchRThreads(threads = 24)
addArchRGenome("hg38")
```

```{r}
proj_K27me3 <- loadArchRProject(path = "./ArchRProject_PBMCs_Combined_Beds_H3K27me3_Doublets_Removed_021126", force = FALSE, showLogo = TRUE)

getEmbedding(ArchRProj = proj_K27me3, embedding = "UMAP_Harmony", returnDF = TRUE)
```

```{r}
proj_K27me3 <- addClusters(
    input = proj_K27me3,
    method = "Seurat",
    name = "Clusters",
    reducedDims = "Harmony",
    resolution = 1,
    maxClusters = 10,
    verbose = FALSE,
    force = TRUE
)
```

```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj_K27me3, colorBy = "cellColData",
    name = "Clusters",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```


```{r}
# CLustering for resolution = 1, maxClusters = 15

## I USED THIS ONE##

proj_K27me3$NewClusters <- ifelse(proj_K27me3$Clusters %in% c("C3", "C6", "C7", "C8", "C10"), "TCell",
    ifelse(proj_K27me3$Clusters %in% c("C1"), "Monocyte",
        ifelse(proj_K27me3$Clusters %in% c("C4", "C5"), "BCell",
            ifelse(proj_K27me3$Clusters %in% c("C2", "C9"), "NKCell",
                "Other"
            )
        )
    )
)

# Check the new clusters
table(proj_K27me3$NewClusters)
```


```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj_K27me3, colorBy = "cellColData",
    name = "NewClusters",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```
```{r}
# 1) Extract barcodes + NewClusters
df_clusters <- data.frame(
    barcode = rownames(getCellColData(proj_K27me3)),
    NewClusters = getCellColData(proj_K27me3)$NewClusters,
    stringsAsFactors = FALSE
)

# (optional) sanity check
table(df_clusters$NewClusters)

# 2) Write out
write.table(
    df_clusters,
    file = "proj_K27me3_barcodes_NewClusters.tsv",
    sep = "\t",
    quote = FALSE,
    row.names = FALSE
)
```


```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj_K27me3, colorBy = "cellColData",
    name = "Clusters",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```

```{r}
# proj_K27me3 <- addGeneScoreMatrix(proj_K27me3, force = TRUE) #, , useTSS = TRUE

# proj_K27me3 <- addImputeWeights(proj_K27me3)
```

```{r}
proj_K4me3 <- loadArchRProject(path = "./tmp/ArchRProject_PBMCs_Combined_Beds_H3K4me3_Doublets_Removed_021126", force = FALSE, showLogo = TRUE)

getEmbedding(ArchRProj = proj_K4me3, embedding = "UMAP_Harmony", returnDF = TRUE)
```


```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj_K4me3, colorBy = "cellColData",
    name = "Clusters",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```


```{r}
proj_K4me3 <- addClusters(
    input = proj_K4me3,
    method = "Seurat",
    name = "Clusters",
    reducedDims = "Harmony",
    resolution = 1,
    maxClusters = 10,
    verbose = FALSE,
    force = TRUE
)
```

```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj_K4me3, colorBy = "cellColData",
    name = "Clusters",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```


```{r}
# CLustering for resolution = 1, maxClusters = 15

## I USED THIS ONE##

proj_K4me3$NewClusters <- ifelse(proj_K4me3$Clusters %in% c("C4", "C5", "C6", "C7", "C8", "C9", "C10"), "TCell",
    ifelse(proj_K4me3$Clusters %in% c("C1"), "Monocyte",
        ifelse(proj_K4me3$Clusters %in% c("C3"), "BCell",
            ifelse(proj_K4me3$Clusters %in% c("C2"), "NKCell",
                "Other"
            )
        )
    )
)

# Check the new clusters
table(proj_K4me3$NewClusters)
```

```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj_K4me3, colorBy = "cellColData",
    name = "NewClusters",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```



```{r}
# 1) Extract barcodes + NewClusters
df_clusters <- data.frame(
    barcode = rownames(getCellColData(proj_K4me3)),
    NewClusters = getCellColData(proj_K4me3)$NewClusters,
    stringsAsFactors = FALSE
)

# (optional) sanity check
table(df_clusters$NewClusters)

# 2) Write out
write.table(
    df_clusters,
    file = "proj_K4me3_barcodes_NewClusters.tsv",
    sep = "\t",
    quote = FALSE,
    row.names = FALSE
)
```







```{r}
# 1. Extract barcodes
proj_K27me3$bc <- sapply(strsplit(proj_K27me3$cellNames, "#"), `[`, 2)
proj_K4me3$bc <- sapply(strsplit(proj_K4me3$cellNames, "#"), `[`, 2)

# 2. Remove duplicate barcodes
proj_K27me3 <- proj_K27me3[!duplicated(proj_K27me3$bc)]
proj_K4me3 <- proj_K4me3[!duplicated(proj_K4me3$bc)]

# 3. Intersect barcodes
common_barcodes <- intersect(proj_K27me3$bc, proj_K4me3$bc)

# 4. Subset to shared barcodes only
proj_K27me3 <- proj_K27me3[proj_K27me3$bc %in% common_barcodes]
proj_K4me3 <- proj_K4me3[proj_K4me3$bc %in% common_barcodes]

# 5. Sort by barcode to ensure matched ordering
proj_K27me3 <- proj_K27me3[order(proj_K27me3$bc)]
proj_K4me3 <- proj_K4me3[order(proj_K4me3$bc)]

# 6. Final check
stopifnot(identical(proj_K27me3$bc, proj_K4me3$bc))
```

```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj_K27me3, colorBy = "cellColData",
    name = "Clusters",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```
```{r}
# Get the total number of cells in the ArchR project
num_cells <- nCells(proj_K27me3)

# Print the number of cells
cat("Number of cells in the ArchR project:", num_cells, "\n")
```



```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj_K4me3, colorBy = "cellColData",
    name = "Clusters",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```
```{r}
# Get the total number of cells in the ArchR project
num_cells <- nCells(proj_K4me3)

# Print the number of cells
cat("Number of cells in the ArchR project:", num_cells, "\n")
```


```{r}
### THIS ONE EXPORTS THE HARMONIZED EMBEDDING ###

export_proj <- function(proj, out_dir) {
    dir.create(file.path(out_dir, "gene_scores"), showWarnings = FALSE, recursive = TRUE)

    # Export metadata and reduced dimensions
    write.csv(getReducedDims(proj), file.path(out_dir, "svd.csv"), quote = FALSE)

    # Export UMAP on Harmony embedding (not default UMAP)
    harmony_umap <- getEmbedding(proj, embedding = "UMAP_Harmony")
    write.csv(harmony_umap, file.path(out_dir, "umap_harmony.csv"), quote = FALSE)

    # Export cell metadata
    write.csv(getCellColData(proj), file.path(out_dir, "cell_metadata.csv"), quote = FALSE)

    # Export gene scores
    gene_scores <- getMatrixFromProject(proj, useMatrix = "GeneScoreMatrix")
    score_matrix <- assays(gene_scores)[["GeneScoreMatrix"]]

    writeMM(score_matrix, file.path(out_dir, "gene_scores", "scores.mtx"))
    write.csv(colnames(score_matrix), file.path(out_dir, "gene_scores", "cells.csv"), quote = FALSE, row.names = FALSE)
    write.csv(rowData(gene_scores)$name, file.path(out_dir, "gene_scores", "genes.csv"), quote = FALSE, row.names = FALSE)
}
```

```{r}
export_proj(proj_K27me3, "./tmp/Export_K27me3_PBMCs_Combined_Beds_Harmony_021126")
export_proj(proj_K4me3, "./tmp/Export_K4me3_PBMCs_Combined_Beds_Harmony_021126")
```

H3K4me3_Doublets_Removed_010126
