---
title: "ArchR CoCnT PBMC H3K27me3 Doublet Removal Workflow"
output: html_notebook
---

## PBMC H3K27me3 Workflow Files

### Input Files

- `../data/Janssens_Lab_Data/PBMCs_Combined_Beds/PBMC_CoCnT_K27me3_H1_010126.bed.gz`
- `../data/Janssens_Lab_Data/PBMCs_Combined_Beds/PBMC_CoCnT_K27me3_H11_010126.bed.gz`
- `../data/Janssens_Lab_Data/PBMCs_Combined_Beds/PBMC_CoCnT_K27me3_H18_010126.bed.gz`
- `../data/Janssens_Lab_Data/PBMCs_Combined_Beds/PBMC_CoCnT_K27me3_H19_010126.bed.gz`
- `../data/Janssens_Lab_Data/PBMCs_Combined_Beds/ArrowFiles/PBMC_CoCnT_K27me3_H1_010126.arrow`
- `../data/Janssens_Lab_Data/PBMCs_Combined_Beds/ArrowFiles/PBMC_CoCnT_K27me3_H11_010126.arrow`
- `../data/Janssens_Lab_Data/PBMCs_Combined_Beds/ArrowFiles/PBMC_CoCnT_K27me3_H18_010126.arrow`
- `../data/Janssens_Lab_Data/PBMCs_Combined_Beds/ArrowFiles/PBMC_CoCnT_K27me3_H19_010126.arrow`


### Output Files And Directories

- ArchR projects (intermediate and final):
  * `./tmp/ArrowFiles/` — Arrow files created from bed input
  * `./tmp/ArchRProjects_PBMC_H3K27me3_Doublet_Removal/` — initial project (all cells, pre-filter)
  * `./tmp/ArchRProject_PBMCs_Combined_Beds_H3K27me3_250reads_010126/` — after fragment count filter (>250 reads) and doublet scoring
  * `./tmp/ArchRProject_PBMCs_Combined_Beds_H3K27me3_Doublets_Removed_010126/` — after round 1 doublet cluster removal
  * `./tmp/ArchRProject_PBMCs_Combined_Beds_H3K27me3_Doublets_Removed_021126/` — after round 2 doublet cluster removal

- Figures:
  * `./figures/H3K27me3_UMAP_DoubletCall_021226.png`
  * `./figures/PBMC_H3K27me3_ArchR_Doublets_RankOrder_021226_DR.png`
  * `./figures/PBMC_H3K27me3_ArchR_Doublets_RankOrder_R2_010126.png`
  * `./figures/PBMC_H3K27me3_ArchR_Doublets_RankOrder_R3_010126.png`
  * `./figures/PBMC_H3K27me3_ArchR_Doublets_RankOrder_R4_010126.png`
  * `./figures/Proj1_PBMC_H3K27me3_UMAP_AllBlack_010126.png`
  * `./figures/Proj2_PBMC_H3K27me3_UMAP_AllBlack_010126.png`
  * `./figures/Proj2_PBMC_H3K27me3_UMAP_AllBlack_010126_Doublets_Removed_R1.png`
  * `./figures/Proj3_PBMC_H3K27me3_UMAP_AllBlack_010126_Doublets_Removed_R1.png`
  * `./figures/Proj3_PBMC_H3K27me3_UMAP_AllBlack_010126_Doublets_Removed_R2.png`
  * `./figures/Proj4_PBMC_H3K27me3_UMAP_AllBlack_010126_Doublets_Removed_R2.png`
  * `./figures/Proj4_PBMC_H3K27me3_UMAP_AllBlack_010126_Doublets_Removed_R3.png`
  * `./figures/Proj5_PBMC_H3K27me3_UMAP_AllBlack_010126_Doublets_Removed_R3.png`
  * `./figures/Proj7_PBMC_H3K27me3_UMAP_AllBlack_010126_Doublets_Removed.png`
  * `./figures/Proj8_PBMC_H3K27me3_UMAP_AllBlack_010126_Doublets_Removed.png`
  * `./figures/Proj9_PBMC_H3K27me3_UMAP_AllBlack_010126_Doublets_Removed.png`
  * `./figures/Proj10_PBMC_H3K27me3_UMAP_AllBlack_010126_Doublets_Removed.png`




```{r, eval=F}
# install_path <- "/home/derek.janssens/R/x86_64-pc-linux-gnu-library/4.4"
# .libPaths(install_path)
# print(.libPaths(install_path))
# install.packages("devtools", lib = install_path)
# install.packages("Seurat", lib = install_path)
# Install ArchR
# if (!requireNamespace("BiocManager", quietly = TRUE)) install.packages("BiocManager", lib = install_path)
# devtools::install_github("GreenleafLab/ArchR", ref = "master",
# 1                         repos = BiocManager::repositories(), lib = install_path)
# install.packages("repr", lib = install_path)
# ArchR::installExtraPackages()
# devtools::install_github("immunogenomics/harmony", lib = install_path)
# Install GenomicRanges and rtracklayer if not already installed
# if (!requireNamespace("GenomicRanges", quietly = TRUE)) {
#  install.packages("BiocManager")
#  BiocManager::install("GenomicRanges")
# }
# if (!requireNamespace("rtracklayer", quietly = TRUE)) {
#  BiocManager::install("rtracklayer")
# }
# install.packages("viridis")
```


```{r}
Sys.unsetenv("DISPLAY")

suppressPackageStartupMessages({
    library(ArchR)
    library(parallel)
    library(rtracklayer)
    library(repr)
    library(dplyr)
    library(plyr)
    library(Seurat)
    library(ggplot2)
    library(GenomicRanges)
    library(rtracklayer)
})
set.seed(1)

# Set default plot size
options(repr.plot.width = 10, repr.plot.height = 10)
```

```{r}
addArchRThreads(threads = 20)
addArchRGenome("hg38")
```

```{r}
# set project name and set sample names to the H3K27me3.bed.gz files

proj_name <- "PBMC_H3K27me3_Doublet_Removal"

sample_name1 <- "PBMC_CoCnT_K27me3_H1_010126"
sample_name2 <- "PBMC_CoCnT_K27me3_H11_010126"
sample_name3 <- "PBMC_CoCnT_K27me3_H18_010126"
sample_name4 <- "PBMC_CoCnT_K27me3_H19_010126"
```


```{r}
# For H3K27me3 set tilematparams (genomics bin size) to 50000 (50kb)
tilematparams <- list(50000, FALSE)
names(tilematparams) <- c("tileSize", "binarize")
```

```{r}
# Set the directory to the location of the bed files, and specify the input files.

wdir <- "../data/Janssens_Lab_Data/PBMCs_Combined_Beds/"

# vector of your dataset name variables
sample_names <- c(sample_name1, sample_name2, sample_name3, sample_name4)
#

# build the full paths and name them
inputFiles <- setNames(
    paste0(wdir, sample_names, ".bed.gz"),
    sample_names
)
```


```{r}
dir.create("./tmp/ArrowFiles/", recursive = TRUE, showWarnings = FALSE)
old_dir <- getwd()
setwd("./tmp/ArrowFiles/")

# Create Arrow files
ArrowFiles <- createArrowFiles(
    inputFiles = inputFiles,
    sampleNames = names(inputFiles),
    # filterTSS = 1, # depricaTRUEd to minTSS
    minTSS = 0, # Dont set this too high because you can always increase later
    # filterFrags = 3000, # depricated to minFrags
    minFrags = 0,
    maxFrags = Inf,
    addTileMat = TRUE,
    addGeneScoreMat = FALSE,
    excludeChr = c("chrM"),
    TileMatParams = tilematparams # ,
    # force = TRUE
    # removeFilteredCells = TRUE # seems to be removed with the other filter args
)

setwd(old_dir)
```




```{r}
# For some reason AE_Hs_Ms_K27me3(H11)_wRb_K4me3(H2)_12XS_12XM_041725.arrow consistently had problems even after remaking the arrow file.

# Combine Arrow files from H3K27me3 into proj_K27me3
arrows_PBMC_1 <- "./tmp/ArrowFiles/PBMC_CoCnT_K27me3_H1_010126.arrow"

arrows_PBMC_2 <- "./tmp/ArrowFiles/PBMC_CoCnT_K27me3_H11_010126.arrow"

arrows_PBMC_3 <- "./tmp/ArrowFiles/PBMC_CoCnT_K27me3_H18_010126.arrow"

arrows_PBMC_4 <- "./tmp/ArrowFiles/PBMC_CoCnT_K27me3_H19_010126.arrow"


inputFiles <- structure(
    c(
        arrows_PBMC_1,
        arrows_PBMC_2,
        arrows_PBMC_3,
        arrows_PBMC_4
    ),
    .Names = c(
        "PBMC_1",
        "PBMC_2",
        "PBMC_3",
        "PBMC_4"
    )
)

proj <- ArchRProject(
    ArrowFiles = inputFiles,
    outputDirectory = "./tmp/ArchRProjects_PBMC_H3K27me3_Doublet_Removal/",
    copyArrows = FALSE,
    showLogo = TRUE
)
```


```{r}
# plot frag distribution
low_cutoff <- 250
hi_cutoff <- 50000

hist(log10(getCellColData(proj[(proj$Sample == "PBMC_CoCnT_K27me3_H1_010126")])$nFrags), breaks = 100)
# hist(log10(getCellColData(proj[(proj$Sample == 'PBMC_CoCnT_K27me3_H11_010126')])$nFrags), breaks = 100)
# hist(log10(getCellColData(proj[(proj$Sample == 'PBMC_CoCnT_K27me3_H18_010126')])$nFrags), breaks = 100)
# hist(log10(getCellColData(proj[(proj$Sample == 'PBMC_CoCnT_K27me3_H19_010126')])$nFrags), breaks = 100)
abline(v = log10(low_cutoff), col = "blue", lwd = 0.5)
abline(v = log10(hi_cutoff), col = "red", lwd = 0.5)
```
```{r}
# plot frag distribution
low_cutoff <- 250
hi_cutoff <- 50000

# hist(log10(getCellColData(proj[(proj$Sample == 'PBMC_CoCnT_K27me3_H1_010126')])$nFrags), breaks = 100)
hist(log10(getCellColData(proj[(proj$Sample == "PBMC_CoCnT_K27me3_H11_010126")])$nFrags), breaks = 100)
# hist(log10(getCellColData(proj[(proj$Sample == 'PBMC_CoCnT_K27me3_H18_010126')])$nFrags), breaks = 100)
# hist(log10(getCellColData(proj[(proj$Sample == 'PBMC_CoCnT_K27me3_H19_010126')])$nFrags), breaks = 100)
abline(v = log10(low_cutoff), col = "blue", lwd = 0.5)
abline(v = log10(hi_cutoff), col = "red", lwd = 0.5)
```

```{r}
# plot frag distribution
low_cutoff <- 250
hi_cutoff <- 50000

# hist(log10(getCellColData(proj[(proj$Sample == 'PBMC_CoCnT_K27me3_H1_010126')])$nFrags), breaks = 100)
# hist(log10(getCellColData(proj[(proj$Sample == 'PBMC_CoCnT_K27me3_H11_010126')])$nFrags), breaks = 100)
hist(log10(getCellColData(proj[(proj$Sample == "PBMC_CoCnT_K27me3_H18_010126")])$nFrags), breaks = 100)
# hist(log10(getCellColData(proj[(proj$Sample == 'PBMC_CoCnT_K27me3_H19_010126')])$nFrags), breaks = 100)
abline(v = log10(low_cutoff), col = "blue", lwd = 0.5)
abline(v = log10(hi_cutoff), col = "red", lwd = 0.5)
```

```{r}
# plot frag distribution
low_cutoff <- 250
hi_cutoff <- 50000

# hist(log10(getCellColData(proj[(proj$Sample == 'PBMC_CoCnT_K27me3_H1_010126')])$nFrags), breaks = 100)
# hist(log10(getCellColData(proj[(proj$Sample == 'PBMC_CoCnT_K27me3_H11_010126')])$nFrags), breaks = 100)
# hist(log10(getCellColData(proj[(proj$Sample == 'PBMC_CoCnT_K27me3_H18_010126')])$nFrags), breaks = 100)
hist(log10(getCellColData(proj[(proj$Sample == "PBMC_CoCnT_K27me3_H19_010126")])$nFrags), breaks = 100)
abline(v = log10(low_cutoff), col = "blue", lwd = 0.5)
abline(v = log10(hi_cutoff), col = "red", lwd = 0.5)
```
```{r}
# Get the total number of cells in the ArchR project
num_cells <- nCells(proj)

# Print the number of cells
cat("Number of cells in the ArchR project:", num_cells, "\n")
```

```{r}
# subset proj and catalogue
proj <- proj[((proj$nFrags > low_cutoff) == TRUE)]

# proj_2 = proj[((proj$nFrags > low_cutoff) == TRUE) & ((proj$nFrags < hi_cutoff) == TRUE)]
```

```{r}
# Get the total number of cells in the ArchR project
num_cells <- nCells(proj)

# Print the number of cells
cat("Number of cells in the ArchR project:", num_cells, "\n")
```





```{r}
# SVD, UMAP, and Clustering including Batch Correction using Harmony

UMAP_Harmony_clusters <- function(proj) {
    # SVD
    proj <- addIterativeLSI(
        ArchRProj = proj,
        useMatrix = "TileMatrix",
        name = "IterativeLSI",
        iterations = 2,
        dimsToUse = 1:15,
        ## if 200000 is too high, set it 20000
        varFeatures = 200000,
        clusterParams = list( # See Seurat::FindClusters,
            resolution = c(0.1, 0.3),
            sampleCells = 8000,
            n.start = 10
        ),
        outlierQuantiles = c(0.025, 0.975),
        verbose = TRUE,
        force = TRUE
    )
    # UMAP
    proj <- addUMAP(
        ArchRProj = proj,
        reducedDims = "IterativeLSI",
        name = "UMAP",
        nNeighbors = 40,
        minDist = 0.4,
        metric = "cosine",
        verbose = FALSE,
        force = TRUE
    )

    proj <- addHarmony(
        ArchRProj = proj,
        reducedDims = "IterativeLSI", # The dimension reduction to use (e.g., IterativeLSI or PCA)
        name = "Harmony", # Name of the batch-corrected reducedDims to save
        groupBy = "Sample", # The batch variable to correct
        force = TRUE
    )

    # Add UMAP using Harmony-Corrected Dimensions
    proj <- addUMAP(
        ArchRProj = proj,
        reducedDims = "Harmony", # Use the Harmony-corrected reducedDims
        name = "UMAP_Harmony", # Name for the UMAP embedding
        nNeighbors = 40, # Number of neighbors
        minDist = 0.4, # Minimum distance for UMAP
        metric = "cosine", # Distance metric for UMAP
        force = TRUE
    )
    proj <- addClusters(
        input = proj,
        method = "Seurat",
        name = "Clusters",
        reducedDims = "Harmony",
        resolution = 20,
        maxClusters = 100,
        verbose = FALSE,
        force = TRUE
    )

    # Save
    # p1 <- plotEmbedding(ArchRProj = proj, colorBy = "cellColData", name = "Clusters", embedding = "UMAP")
    # plotPDF(p1, name = "Plot-UMAP-Sample-Clusters_1.pdf", ArchRProj = proj, addDOC = FALSE, width = 5, height = 5)
    return(proj)
}
```

```{r}
# UMAP + clustering over all cells and catalogue
proj <- UMAP_Harmony_clusters(proj)
```


```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj, colorBy = "cellColData",
    name = "nFrags",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```


```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj, colorBy = "cellColData",
    name = "Sample",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```



```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj, colorBy = "cellColData",
    name = "TSSEnrichment",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```





```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj, colorBy = "cellColData",
    name = "Clusters",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```




```{r}
proj <- addDoubletScores(
    input = proj,
    useMatrix = "TileMatrix",
    k = 10,
    # nTrials = 5,
    dimsToUse = 1:15,
    LSIMethod = 1,
    scaleDims = FALSE,
    corCutOff = 0.75,
    knnMethod = "UMAP_Harmony",
    UMAPParams = list(
        n_neighbors = 40, min_dist = 0.4, metric = "euclidean", verbose =
            FALSE
    ),
    LSIParams = list(outlierQuantiles = NULL, filterBias = FALSE),
    # outDir = getOutputDirectory(input),
    # threads = getArchRThreads(),
    force = FALSE,
    parallelParam = NULL,
    verbose = TRUE,
    logFile = createLogFile("addDoubletScores")
)
```


```{r}
saveArchRProject(
    ArchRProj = proj,
    outputDirectory = "./tmp/ArchRProject_PBMCs_Combined_Beds_H3K27me3_250reads_010126/",
    overwrite = TRUE,
    load = TRUE,
    dropCells = FALSE,
    logFile = createLogFile("saveArchRProject"),
    threads = getArchRThreads()
)
```

```{r}
proj <- loadArchRProject(path = "./tmp/ArchRProject_PBMCs_Combined_Beds_H3K27me3_250reads_010126/", force = FALSE, showLogo = TRUE)

getEmbedding(ArchRProj = proj, embedding = "UMAP_Harmony", returnDF = TRUE)
```


```{r}
proj <- addClusters(
    input = proj,
    method = "Seurat",
    name = "Clusters",
    reducedDims = "Harmony",
    resolution = 2,
    maxClusters = 25,
    verbose = FALSE,
    force = TRUE
)
```

```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj, colorBy = "cellColData",
    name = "Clusters",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```
```{r}
colnames(getCellColData(proj))
```


```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj, colorBy = "cellColData",
    name = "DoubletEnrichment",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```

```{r}
library(ggplot2)
library(dplyr)

# Extract UMAP coordinates from ArchR object
umap_df <- proj@cellColData %>% data.frame()
umap_df$UMAP_1 <- proj@embeddings$UMAP_Harmony$df[, 1]
umap_df$UMAP_2 <- proj@embeddings$UMAP_Harmony$df[, 2]

# Define the output file path
output_file <- "./figures/Proj1_PBMC_H3K27me3_UMAP_AllBlack_010126.png"

# Plot all cells in black
umap_plot_black <- ggplot(umap_df, aes(x = UMAP_1, y = UMAP_2)) +
    geom_point(color = "black", size = 0.5) +
    theme_void() +
    theme(
        legend.position = "none",
        plot.title = element_blank(),
        strip.text = element_blank(),
        panel.border = element_rect(color = "black", fill = NA, linewidth = 1.2)
    )

# Save the UMAP plot
ggsave(
    filename = output_file,
    plot = umap_plot_black,
    device = "png",
    width = 6,
    height = 6,
    dpi = 300
)

# Also print it to screen
print(umap_plot_black)
```



```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj, colorBy = "cellColData",
    name = "Clusters",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```
```{r}
# UMAP colored by singlet/doublet call (DoubletEnrichment threshold)
library(dplyr)
library(ggplot2)

# 1) Build df with UMAP + metadata
df <- proj@cellColData %>% as.data.frame()
df$UMAP_1 <- proj@embeddings$UMAP_Harmony$df[, 1]
df$UMAP_2 <- proj@embeddings$UMAP_Harmony$df[, 2]

# Make sure these columns exist in df; otherwise adjust names
# (often already in cellColData)
# df$DoubletEnrichment <- df$DoubletEnrichment

# 2) Call doublets vs singlets
threshold <- 2
df$call <- ifelse(df$DoubletEnrichment > threshold, "doublet", "singlet")
df$call <- factor(df$call, levels = c("singlet", "doublet"))

# 3) Plot
output_file <- "./figures/H3K27me3_UMAP_DoubletCall_021226.png"

p <- ggplot(df, aes(x = UMAP_1, y = UMAP_2, color = call)) +
    geom_point(size = 0.5) +
    theme_void() +
    theme(
        plot.title = element_blank(),
        strip.text = element_blank(),
        legend.position = "right",
        legend.text = element_text(size = 10),
        legend.title = element_text(size = 12, face = "bold")
    ) +
    scale_color_manual(
        values = c("singlet" = "steelblue", "doublet" = "red"),
        name = "Doublet call"
    )

ggsave(
    filename = output_file,
    plot = p,
    device = "png",
    width = 6,
    height = 6,
    dpi = 300
)

print(p)
```
```{r}
library(ArchR)
library(dplyr)
library(ggplot2)

# 1. Extract metadata
df <- data.frame(getCellColData(proj, select = c("DoubletEnrichment", "Clusters")))

# 2. Call doublets (OPTION 1: threshold-based)
df$call <- ifelse(df$DoubletEnrichment > 2, "doublet", "singlet") # adjust threshold as needed

# 2b. (OPTION 2: quantile-based cutoff)
# quantile_cutoff <- quantile(df$DoubletEnrichment, 0.95)
# df$call <- ifelse(df$DoubletEnrichment > quantile_cutoff, "doublet", "singlet")

# 3. Calculate percentage of doublets per cluster
df_summary <- df %>%
    dplyr::group_by(Clusters, call) %>%
    dplyr::tally() %>%
    dplyr::group_by(Clusters) %>%
    dplyr::mutate(
        total = sum(n),
        perc = n / total * 100
    ) %>%
    dplyr::filter(call == "doublet") %>%
    dplyr::arrange(desc(perc))


# 4. Plot rank-ordered dot plot
rank_order_dot_plot <- ggplot(df_summary, aes(x = reorder(Clusters, -perc), y = perc)) +
    geom_point(size = 6, color = "steelblue") +
    geom_hline(yintercept = 20, color = "red", linetype = "dotted", size = 3) +
    theme_bw() +
    theme(
        axis.text.x = element_text(angle = 45, hjust = 1),
        panel.grid = element_blank(),
        panel.border = element_rect(size = 3, color = "black")
    ) +
    labs(
        x = "Cluster",
        y = "Percentage of Doublets (%)",
        title = "Percentage of ArchR-Inferred Doublets by Cluster (Rank-Ordered)"
    )

# 5. Show and save plot
print(rank_order_dot_plot)

ggsave(
    filename = "./figures/PBMC_H3K27me3_ArchR_Doublets_RankOrder_021226_DR.png",
    plot = rank_order_dot_plot,
    device = "png",
    width = 8,
    height = 6,
    dpi = 300
)

# Optional: Remove doublet-prone clusters
# high_doublet_clusters <- df_summary$Clusters[df_summary$perc > 15]
# proj <- proj[!(proj$Clusters %in% high_doublet_clusters)]
```


```{r}
# Get the total number of cells in the ArchR project
num_cells <- nCells(proj)

# Print the number of cells
cat("Number of cells in the ArchR project:", num_cells, "\n")
```

```{r}
# Identify and remove high-doublet clusters (> 8.5%)
high_doublet_clusters <- df_summary$Clusters[df_summary$perc > 20]
message("Removing clusters with >8.5% doublets: ", paste(high_doublet_clusters, collapse = ", "))

proj_2 <- proj[!(proj$Clusters %in% high_doublet_clusters), ]

# Optional: verify removal
table(proj_2$Clusters)
```

```{r}
# Get the total number of cells in the ArchR project
num_cells <- nCells(proj_2)

# Print the number of cells
cat("Number of cells in the ArchR project:", num_cells, "\n")
```



```{r}
library(ggplot2)
library(dplyr)

# Extract UMAP coordinates from ArchR object
umap_df <- proj_2@cellColData %>% data.frame()
umap_df$UMAP_1 <- proj_2@embeddings$UMAP_Harmony$df[, 1]
umap_df$UMAP_2 <- proj_2@embeddings$UMAP_Harmony$df[, 2]

# Define the output file path
output_file <- "./figures/Proj2_PBMC_H3K27me3_UMAP_AllBlack_010126.png"

# Plot all cells in black
umap_plot_black <- ggplot(umap_df, aes(x = UMAP_1, y = UMAP_2)) +
    geom_point(color = "black", size = 0.5) +
    theme_void() +
    theme(
        legend.position = "none",
        plot.title = element_blank(),
        strip.text = element_blank(),
        panel.border = element_rect(color = "black", fill = NA, linewidth = 1.2)
    )

# Save the UMAP plot
ggsave(
    filename = output_file,
    plot = umap_plot_black,
    device = "png",
    width = 6,
    height = 6,
    dpi = 300
)

# Also print it to screen
print(umap_plot_black)
```

```{r}
# UMAP + clustering over all cells and catalogue
proj_2 <- UMAP_Harmony_clusters(proj_2)
```


```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj_2, colorBy = "cellColData",
    name = "Sample",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```


```{r}
proj_2 <- addClusters(
    input = proj_2,
    method = "Seurat",
    name = "Clusters",
    reducedDims = "Harmony",
    resolution = 2,
    maxClusters = 25,
    verbose = FALSE,
    force = TRUE
)
```

```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj_2, colorBy = "cellColData",
    name = "Clusters",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```


```{r}
library(ArchR)
library(dplyr)
library(ggplot2)

# 1. Extract metadata
df <- data.frame(getCellColData(proj_2, select = c("DoubletEnrichment", "Clusters")))

# 2. Call doublets (OPTION 1: threshold-based)
df$call <- ifelse(df$DoubletEnrichment > 2, "doublet", "singlet") # adjust threshold as needed

# 2b. (OPTION 2: quantile-based cutoff)
# quantile_cutoff <- quantile(df$DoubletEnrichment, 0.95)
# df$call <- ifelse(df$DoubletEnrichment > quantile_cutoff, "doublet", "singlet")

# 3. Calculate percentage of doublets per cluster
df_summary <- df %>%
    dplyr::group_by(Clusters, call) %>%
    dplyr::tally() %>%
    dplyr::group_by(Clusters) %>%
    dplyr::mutate(
        total = sum(n),
        perc = n / total * 100
    ) %>%
    dplyr::filter(call == "doublet") %>%
    dplyr::arrange(desc(perc))


# 4. Plot rank-ordered dot plot
rank_order_dot_plot <- ggplot(df_summary, aes(x = reorder(Clusters, -perc), y = perc)) +
    geom_point(size = 3, color = "steelblue") +
    geom_hline(yintercept = 20, color = "red", linetype = "dotted", size = 1.2) +
    theme_bw() +
    theme(
        axis.text.x = element_text(angle = 45, hjust = 1),
        panel.grid = element_blank(),
        panel.border = element_rect(size = 1.5, color = "black")
    ) +
    labs(
        x = "Cluster",
        y = "Percentage of Doublets (%)",
        title = "Percentage of ArchR-Inferred Doublets by Cluster (Rank-Ordered)"
    )

# 5. Show and save plot
print(rank_order_dot_plot)

ggsave(
    filename = "./figures/PBMC_H3K27me3_ArchR_Doublets_RankOrder_R2_010126.png",
    plot = rank_order_dot_plot,
    device = "png",
    width = 8,
    height = 6,
    dpi = 300
)

# Optional: Remove doublet-prone clusters
# high_doublet_clusters <- df_summary$Clusters[df_summary$perc > 15]
# proj <- proj[!(proj$Clusters %in% high_doublet_clusters)]
```


```{r}
# Get the total number of cells in the ArchR project
num_cells <- nCells(proj_2)

# Print the number of cells
cat("Number of cells in the ArchR project:", num_cells, "\n")
```

```{r}
# Identify and remove high-doublet clusters (> 8.5%)
high_doublet_clusters <- df_summary$Clusters[df_summary$perc > 20]
message("Removing clusters with >8.5% doublets: ", paste(high_doublet_clusters, collapse = ", "))

proj_3 <- proj_2[!(proj_2$Clusters %in% high_doublet_clusters), ]

# Optional: verify removal
table(proj_3$Clusters)
```

```{r}
# Get the total number of cells in the ArchR project
num_cells <- nCells(proj_3)

# Print the number of cells
cat("Number of cells in the ArchR project:", num_cells, "\n")
```

```{r}
library(ggplot2)
library(dplyr)

# Extract UMAP coordinates from ArchR object
umap_df <- proj_2@cellColData %>% data.frame()
umap_df$UMAP_1 <- proj_2@embeddings$UMAP_Harmony$df[, 1]
umap_df$UMAP_2 <- proj_2@embeddings$UMAP_Harmony$df[, 2]

# Define the output file path
output_file <- "./figures/Proj2_PBMC_H3K27me3_UMAP_AllBlack_010126_Doublets_Removed_R1.png"

# Plot all cells in black
umap_plot_black <- ggplot(umap_df, aes(x = UMAP_1, y = UMAP_2)) +
    geom_point(color = "black", size = 0.5) +
    theme_void() +
    theme(
        legend.position = "none",
        plot.title = element_blank(),
        strip.text = element_blank(),
        panel.border = element_rect(color = "black", fill = NA, linewidth = 1.2)
    )

# Save the UMAP plot
ggsave(
    filename = output_file,
    plot = umap_plot_black,
    device = "png",
    width = 6,
    height = 6,
    dpi = 300
)

# Also print it to screen
print(umap_plot_black)
```







```{r}
library(ggplot2)
library(dplyr)

# Extract UMAP coordinates from ArchR object
umap_df <- proj_3@cellColData %>% data.frame()
umap_df$UMAP_1 <- proj_3@embeddings$UMAP_Harmony$df[, 1]
umap_df$UMAP_2 <- proj_3@embeddings$UMAP_Harmony$df[, 2]

# Define the output file path
output_file <- "./figures/Proj3_PBMC_H3K27me3_UMAP_AllBlack_010126_Doublets_Removed_R1.png"

# Plot all cells in black
umap_plot_black <- ggplot(umap_df, aes(x = UMAP_1, y = UMAP_2)) +
    geom_point(color = "black", size = 0.5) +
    theme_void() +
    theme(
        legend.position = "none",
        plot.title = element_blank(),
        strip.text = element_blank(),
        panel.border = element_rect(color = "black", fill = NA, linewidth = 1.2)
    )

# Save the UMAP plot
ggsave(
    filename = output_file,
    plot = umap_plot_black,
    device = "png",
    width = 6,
    height = 6,
    dpi = 300
)

# Also print it to screen
print(umap_plot_black)
```

```{r}
# UMAP + clustering over all cells and catalogue
proj_3 <- UMAP_Harmony_clusters(proj_3)
```




```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj_3, colorBy = "cellColData",
    name = "nFrags",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```



```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj_3, colorBy = "cellColData",
    name = "Sample",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```


```{r}
proj_3 <- addClusters(
    input = proj_3,
    method = "Seurat",
    name = "Clusters",
    reducedDims = "Harmony",
    resolution = 3,
    maxClusters = 40,
    verbose = FALSE,
    force = TRUE
)
```

```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj_3, colorBy = "cellColData",
    name = "Clusters",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```


```{r}
library(ArchR)
library(dplyr)
library(ggplot2)

# 1. Extract metadata
df <- data.frame(getCellColData(proj_3, select = c("DoubletEnrichment", "Clusters")))

# 2. Call doublets (OPTION 1: threshold-based)
df$call <- ifelse(df$DoubletEnrichment > 2, "doublet", "singlet") # adjust threshold as needed

# 2b. (OPTION 2: quantile-based cutoff)
# quantile_cutoff <- quantile(df$DoubletEnrichment, 0.95)
# df$call <- ifelse(df$DoubletEnrichment > quantile_cutoff, "doublet", "singlet")

# 3. Calculate percentage of doublets per cluster
df_summary <- df %>%
    dplyr::group_by(Clusters, call) %>%
    dplyr::tally() %>%
    dplyr::group_by(Clusters) %>%
    dplyr::mutate(
        total = sum(n),
        perc = n / total * 100
    ) %>%
    dplyr::filter(call == "doublet") %>%
    dplyr::arrange(desc(perc))


# 4. Plot rank-ordered dot plot
rank_order_dot_plot <- ggplot(df_summary, aes(x = reorder(Clusters, -perc), y = perc)) +
    geom_point(size = 3, color = "steelblue") +
    geom_hline(yintercept = 18, color = "red", linetype = "dotted", size = 1.2) +
    theme_bw() +
    theme(
        axis.text.x = element_text(angle = 45, hjust = 1),
        panel.grid = element_blank(),
        panel.border = element_rect(size = 1.5, color = "black")
    ) +
    labs(
        x = "Cluster",
        y = "Percentage of Doublets (%)",
        title = "Percentage of ArchR-Inferred Doublets by Cluster (Rank-Ordered)"
    )

# 5. Show and save plot
print(rank_order_dot_plot)

ggsave(
    filename = "./figures/PBMC_H3K27me3_ArchR_Doublets_RankOrder_R3_010126.png",
    plot = rank_order_dot_plot,
    device = "png",
    width = 8,
    height = 6,
    dpi = 300
)

# Optional: Remove doublet-prone clusters
# high_doublet_clusters <- df_summary$Clusters[df_summary$perc > 15]
# proj <- proj[!(proj$Clusters %in% high_doublet_clusters)]
```




```{r}
# Get the total number of cells in the ArchR project
num_cells <- nCells(proj_3)

# Print the number of cells
cat("Number of cells in the ArchR project:", num_cells, "\n")
```

```{r}
# Identify and remove high-doublet clusters (> 8.5%)
high_doublet_clusters <- df_summary$Clusters[df_summary$perc > 18]
message("Removing clusters with >8.5% doublets: ", paste(high_doublet_clusters, collapse = ", "))

proj_4 <- proj_3[!(proj_3$Clusters %in% high_doublet_clusters), ]

# Optional: verify removal
table(proj_4$Clusters)
```

```{r}
# Get the total number of cells in the ArchR project
num_cells <- nCells(proj_4)

# Print the number of cells
cat("Number of cells in the ArchR project:", num_cells, "\n")
```

```{r}
library(ggplot2)
library(dplyr)

# Extract UMAP coordinates from ArchR object
umap_df <- proj_3@cellColData %>% data.frame()
umap_df$UMAP_1 <- proj_3@embeddings$UMAP_Harmony$df[, 1]
umap_df$UMAP_2 <- proj_3@embeddings$UMAP_Harmony$df[, 2]

# Define the output file path
output_file <- "./figures/Proj3_PBMC_H3K27me3_UMAP_AllBlack_010126_Doublets_Removed_R2.png"

# Plot all cells in black
umap_plot_black <- ggplot(umap_df, aes(x = UMAP_1, y = UMAP_2)) +
    geom_point(color = "black", size = 0.5) +
    theme_void() +
    theme(
        legend.position = "none",
        plot.title = element_blank(),
        strip.text = element_blank(),
        panel.border = element_rect(color = "black", fill = NA, linewidth = 1.2)
    )

# Save the UMAP plot
ggsave(
    filename = output_file,
    plot = umap_plot_black,
    device = "png",
    width = 6,
    height = 6,
    dpi = 300
)

# Also print it to screen
print(umap_plot_black)
```







```{r}
library(ggplot2)
library(dplyr)

# Extract UMAP coordinates from ArchR object
umap_df <- proj_4@cellColData %>% data.frame()
umap_df$UMAP_1 <- proj_4@embeddings$UMAP_Harmony$df[, 1]
umap_df$UMAP_2 <- proj_4@embeddings$UMAP_Harmony$df[, 2]

# Define the output file path
output_file <- "./figures/Proj4_PBMC_H3K27me3_UMAP_AllBlack_010126_Doublets_Removed_R2.png"

# Plot all cells in black
umap_plot_black <- ggplot(umap_df, aes(x = UMAP_1, y = UMAP_2)) +
    geom_point(color = "black", size = 0.5) +
    theme_void() +
    theme(
        legend.position = "none",
        plot.title = element_blank(),
        strip.text = element_blank(),
        panel.border = element_rect(color = "black", fill = NA, linewidth = 1.2)
    )

# Save the UMAP plot
ggsave(
    filename = output_file,
    plot = umap_plot_black,
    device = "png",
    width = 6,
    height = 6,
    dpi = 300
)

# Also print it to screen
print(umap_plot_black)
```

```{r}
# UMAP + clustering over all cells and catalogue
proj_4 <- UMAP_Harmony_clusters(proj_4)
```





```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj_4, colorBy = "cellColData",
    name = "Sample",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```


```{r}
proj_4 <- addClusters(
    input = proj_4,
    method = "Seurat",
    name = "Clusters",
    reducedDims = "Harmony",
    resolution = 5,
    maxClusters = 100,
    verbose = FALSE,
    force = TRUE
)
```

```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj_4, colorBy = "cellColData",
    name = "Clusters",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```


```{r}
library(ArchR)
library(dplyr)
library(ggplot2)

# 1. Extract metadata
df <- data.frame(getCellColData(proj_4, select = c("DoubletEnrichment", "Clusters")))

# 2. Call doublets (OPTION 1: threshold-based)
df$call <- ifelse(df$DoubletEnrichment > 2.5, "doublet", "singlet") # adjust threshold as needed

# 2b. (OPTION 2: quantile-based cutoff)
# quantile_cutoff <- quantile(df$DoubletEnrichment, 0.95)
# df$call <- ifelse(df$DoubletEnrichment > quantile_cutoff, "doublet", "singlet")

# 3. Calculate percentage of doublets per cluster
df_summary <- df %>%
    dplyr::group_by(Clusters, call) %>%
    dplyr::tally() %>%
    dplyr::group_by(Clusters) %>%
    dplyr::mutate(
        total = sum(n),
        perc = n / total * 100
    ) %>%
    dplyr::filter(call == "doublet") %>%
    dplyr::arrange(desc(perc))


# 4. Plot rank-ordered dot plot
rank_order_dot_plot <- ggplot(df_summary, aes(x = reorder(Clusters, -perc), y = perc)) +
    geom_point(size = 3, color = "steelblue") +
    geom_hline(yintercept = 5, color = "red", linetype = "dotted", size = 1.2) +
    theme_bw() +
    theme(
        axis.text.x = element_text(angle = 45, hjust = 1),
        panel.grid = element_blank(),
        panel.border = element_rect(size = 1.5, color = "black")
    ) +
    labs(
        x = "Cluster",
        y = "Percentage of Doublets (%)",
        title = "Percentage of ArchR-Inferred Doublets by Cluster (Rank-Ordered)"
    )

# 5. Show and save plot
print(rank_order_dot_plot)

ggsave(
    filename = "./figures/PBMC_H3K27me3_ArchR_Doublets_RankOrder_R4_010126.png",
    plot = rank_order_dot_plot,
    device = "png",
    width = 8,
    height = 6,
    dpi = 300
)

# Optional: Remove doublet-prone clusters
# high_doublet_clusters <- df_summary$Clusters[df_summary$perc > 15]
# proj <- proj[!(proj$Clusters %in% high_doublet_clusters)]
```




```{r}
# Get the total number of cells in the ArchR project
num_cells <- nCells(proj_4)

# Print the number of cells
cat("Number of cells in the ArchR project:", num_cells, "\n")
```

```{r}
# Identify and remove high-doublet clusters (> 8.5%)
# high_doublet_clusters <- df_summary$Clusters[df_summary$perc > 5]
# message("Removing clusters with >8.5% doublets: ", paste(high_doublet_clusters, collapse = ", "))

proj_5 <- proj_4[!(proj_4$Clusters %in% "C14"), ]

# Optional: verify removal
# table(proj_5$Clusters)
```

```{r}
# Get the total number of cells in the ArchR project
num_cells <- nCells(proj_5)

# Print the number of cells
cat("Number of cells in the ArchR project:", num_cells, "\n")
```

```{r}
library(ggplot2)
library(dplyr)

# Extract UMAP coordinates from ArchR object
umap_df <- proj_4@cellColData %>% data.frame()
umap_df$UMAP_1 <- proj_4@embeddings$UMAP_Harmony$df[, 1]
umap_df$UMAP_2 <- proj_4@embeddings$UMAP_Harmony$df[, 2]

# Define the output file path
output_file <- "./figures/Proj4_PBMC_H3K27me3_UMAP_AllBlack_010126_Doublets_Removed_R3.png"

# Plot all cells in black
umap_plot_black <- ggplot(umap_df, aes(x = UMAP_1, y = UMAP_2)) +
    geom_point(color = "black", size = 0.5) +
    theme_void() +
    theme(
        legend.position = "none",
        plot.title = element_blank(),
        strip.text = element_blank(),
        panel.border = element_rect(color = "black", fill = NA, linewidth = 1.2)
    )

# Save the UMAP plot
ggsave(
    filename = output_file,
    plot = umap_plot_black,
    device = "png",
    width = 6,
    height = 6,
    dpi = 300
)

# Also print it to screen
print(umap_plot_black)
```







```{r}
library(ggplot2)
library(dplyr)

# Extract UMAP coordinates from ArchR object
umap_df <- proj_5@cellColData %>% data.frame()
umap_df$UMAP_1 <- proj_5@embeddings$UMAP_Harmony$df[, 1]
umap_df$UMAP_2 <- proj_5@embeddings$UMAP_Harmony$df[, 2]

# Define the output file path
output_file <- "./figures/Proj5_PBMC_H3K27me3_UMAP_AllBlack_010126_Doublets_Removed_R3.png"

# Plot all cells in black
umap_plot_black <- ggplot(umap_df, aes(x = UMAP_1, y = UMAP_2)) +
    geom_point(color = "black", size = 0.5) +
    theme_void() +
    theme(
        legend.position = "none",
        plot.title = element_blank(),
        strip.text = element_blank(),
        panel.border = element_rect(color = "black", fill = NA, linewidth = 1.2)
    )

# Save the UMAP plot
ggsave(
    filename = output_file,
    plot = umap_plot_black,
    device = "png",
    width = 6,
    height = 6,
    dpi = 300
)

# Also print it to screen
print(umap_plot_black)
```

```{r}
# UMAP + clustering over all cells and catalogue
proj_5 <- UMAP_Harmony_clusters(proj_5)
```




```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj_5, colorBy = "cellColData",
    name = "Sample",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```


```{r}
proj_5 <- addClusters(
    input = proj_5,
    method = "Seurat",
    name = "Clusters",
    reducedDims = "Harmony",
    resolution = 4,
    maxClusters = 50,
    verbose = FALSE,
    force = TRUE
)
```

```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj_5, colorBy = "cellColData",
    name = "Clusters",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```
```{r}
# Get the total number of cells in the ArchR project
num_cells <- nCells(proj_5)

# Print the number of cells
cat("Number of cells in the ArchR project:", num_cells, "\n")
```

```{r}
# Identify and remove high-doublet clusters (> 8.5%)
# high_doublet_clusters <- df_summary$Clusters[df_summary$perc > 5]
# message("Removing clusters with >8.5% doublets: ", paste(high_doublet_clusters, collapse = ", "))

proj_6 <- proj_5[!(proj_5$Clusters %in% "C94"), ]

# Optional: verify removal
# table(proj_5$Clusters)
```

```{r}
# Get the total number of cells in the ArchR project
num_cells <- nCells(proj_6)

# Print the number of cells
cat("Number of cells in the ArchR project:", num_cells, "\n")
```



```{r}
# UMAP + clustering over all cells and catalogue
proj_6 <- UMAP_Harmony_clusters(proj_6)
```




```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj_6, colorBy = "cellColData",
    name = "Sample",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```
```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj_6, colorBy = "cellColData",
    name = "Clusters",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```



```{r}
# Get the total number of cells in the ArchR project
num_cells <- nCells(proj_6)

# Print the number of cells
cat("Number of cells in the ArchR project:", num_cells, "\n")
```



```{r}
# Identify and remove high-doublet clusters (> 8.5%)
# high_doublet_clusters <- df_summary$Clusters[df_summary$perc > 5]
# message("Removing clusters with >8.5% doublets: ", paste(high_doublet_clusters, collapse = ", "))

proj_7 <- proj_6[!(proj_6$Clusters %in% "C32"), ]

# Optional: verify removal
# table(proj_5$Clusters)
```

```{r}
# Get the total number of cells in the ArchR project
num_cells <- nCells(proj_7)

# Print the number of cells
cat("Number of cells in the ArchR project:", num_cells, "\n")
```

```{r}
library(ggplot2)
library(dplyr)

# Extract UMAP coordinates from ArchR object
umap_df <- proj_7@cellColData %>% data.frame()
umap_df$UMAP_1 <- proj_7@embeddings$UMAP_Harmony$df[, 1]
umap_df$UMAP_2 <- proj_7@embeddings$UMAP_Harmony$df[, 2]

# Define the output file path
output_file <- "./figures/Proj7_PBMC_H3K27me3_UMAP_AllBlack_010126_Doublets_Removed.png"

# Plot all cells in black
umap_plot_black <- ggplot(umap_df, aes(x = UMAP_1, y = UMAP_2)) +
    geom_point(color = "black", size = 0.5) +
    theme_void() +
    theme(
        legend.position = "none",
        plot.title = element_blank(),
        strip.text = element_blank(),
        panel.border = element_rect(color = "black", fill = NA, linewidth = 1.2)
    )

# Save the UMAP plot
ggsave(
    filename = output_file,
    plot = umap_plot_black,
    device = "png",
    width = 6,
    height = 6,
    dpi = 300
)

# Also print it to screen
print(umap_plot_black)
```

```{r}
# UMAP + clustering over all cells and catalogue
proj_7 <- UMAP_Harmony_clusters(proj_7)
```



```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj_7, colorBy = "cellColData",
    name = "Sample",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```



```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj_7, colorBy = "cellColData",
    name = "Clusters",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```




```{r}
# Get the total number of cells in the ArchR project
num_cells <- nCells(proj_7)

# Print the number of cells
cat("Number of cells in the ArchR project:", num_cells, "\n")
```



```{r}
# Identify and remove high-doublet clusters (> 8.5%)
high_doublet_clusters <- c("C89") # , 'C99'
message("Removing clusters with >8.5% doublets: ", paste(high_doublet_clusters, collapse = ", "))

# Subset ArchRProject to exclude those clusters
proj_8 <- proj_7[!(proj_7$Clusters %in% high_doublet_clusters), ]

# Optional: verify removal
table(proj_8$Clusters)
```

```{r}
# Get the total number of cells in the ArchR project
num_cells <- nCells(proj_8)

# Print the number of cells
cat("Number of cells in the ArchR project:", num_cells, "\n")
```

```{r}
library(ggplot2)
library(dplyr)

# Extract UMAP coordinates from ArchR object
umap_df <- proj_8@cellColData %>% data.frame()
umap_df$UMAP_1 <- proj_8@embeddings$UMAP_Harmony$df[, 1]
umap_df$UMAP_2 <- proj_8@embeddings$UMAP_Harmony$df[, 2]

# Define the output file path
output_file <- "./figures/Proj8_PBMC_H3K27me3_UMAP_AllBlack_010126_Doublets_Removed.png"

# Plot all cells in black
umap_plot_black <- ggplot(umap_df, aes(x = UMAP_1, y = UMAP_2)) +
    geom_point(color = "black", size = 0.5) +
    theme_void() +
    theme(
        legend.position = "none",
        plot.title = element_blank(),
        strip.text = element_blank(),
        panel.border = element_rect(color = "black", fill = NA, linewidth = 1.2)
    )

# Save the UMAP plot
ggsave(
    filename = output_file,
    plot = umap_plot_black,
    device = "png",
    width = 6,
    height = 6,
    dpi = 300
)

# Also print it to screen
print(umap_plot_black)
```

```{r}
# UMAP + clustering over all cells and catalogue
proj_8 <- UMAP_Harmony_clusters(proj_8)
```





```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj_8, colorBy = "cellColData",
    name = "Sample",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```




```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj_8, colorBy = "cellColData",
    name = "Clusters",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```



```{r}
# Get the total number of cells in the ArchR project
num_cells <- nCells(proj_8)

# Print the number of cells
cat("Number of cells in the ArchR project:", num_cells, "\n")
```



```{r}
# Identify and remove high-doublet clusters (> 8.5%)
high_doublet_clusters <- c("C56", "C93") #
message("Removing clusters with >8.5% doublets: ", paste(high_doublet_clusters, collapse = ", "))

# Subset ArchRProject to exclude those clusters
proj_9 <- proj_8[!(proj_8$Clusters %in% high_doublet_clusters), ]

# Optional: verify removal
table(proj_9$Clusters)
```

```{r}
# Get the total number of cells in the ArchR project
num_cells <- nCells(proj_9)

# Print the number of cells
cat("Number of cells in the ArchR project:", num_cells, "\n")
```

```{r}
library(ggplot2)
library(dplyr)

# Extract UMAP coordinates from ArchR object
umap_df <- proj_9@cellColData %>% data.frame()
umap_df$UMAP_1 <- proj_9@embeddings$UMAP_Harmony$df[, 1]
umap_df$UMAP_2 <- proj_9@embeddings$UMAP_Harmony$df[, 2]

# Define the output file path
output_file <- "./figures/Proj9_PBMC_H3K27me3_UMAP_AllBlack_010126_Doublets_Removed.png"

# Plot all cells in black
umap_plot_black <- ggplot(umap_df, aes(x = UMAP_1, y = UMAP_2)) +
    geom_point(color = "black", size = 0.5) +
    theme_void() +
    theme(
        legend.position = "none",
        plot.title = element_blank(),
        strip.text = element_blank(),
        panel.border = element_rect(color = "black", fill = NA, linewidth = 1.2)
    )

# Save the UMAP plot
ggsave(
    filename = output_file,
    plot = umap_plot_black,
    device = "png",
    width = 6,
    height = 6,
    dpi = 300
)

# Also print it to screen
print(umap_plot_black)
```

```{r}
# UMAP + clustering over all cells and catalogue
proj_9 <- UMAP_Harmony_clusters(proj_9)
```





```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj_9, colorBy = "cellColData",
    name = "Sample",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```




```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj_9, colorBy = "cellColData",
    name = "Clusters",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```




```{r}
# Get the total number of cells in the ArchR project
num_cells <- nCells(proj_9)

# Print the number of cells
cat("Number of cells in the ArchR project:", num_cells, "\n")
```



```{r}
# Identify and remove high-doublet clusters (> 8.5%)
high_doublet_clusters <- c("C27", "C46", "C47") #
message("Removing clusters with >8.5% doublets: ", paste(high_doublet_clusters, collapse = ", "))

# Subset ArchRProject to exclude those clusters
proj_10 <- proj_9[!(proj_9$Clusters %in% high_doublet_clusters), ]

# Optional: verify removal
table(proj_10$Clusters)
```

```{r}
# Get the total number of cells in the ArchR project
num_cells <- nCells(proj_10)

# Print the number of cells
cat("Number of cells in the ArchR project:", num_cells, "\n")
```

```{r}
library(ggplot2)
library(dplyr)

# Extract UMAP coordinates from ArchR object
umap_df <- proj_10@cellColData %>% data.frame()
umap_df$UMAP_1 <- proj_10@embeddings$UMAP_Harmony$df[, 1]
umap_df$UMAP_2 <- proj_10@embeddings$UMAP_Harmony$df[, 2]

# Define the output file path
output_file <- "./figures/Proj10_PBMC_H3K27me3_UMAP_AllBlack_010126_Doublets_Removed.png"

# Plot all cells in black
umap_plot_black <- ggplot(umap_df, aes(x = UMAP_1, y = UMAP_2)) +
    geom_point(color = "black", size = 0.5) +
    theme_void() +
    theme(
        legend.position = "none",
        plot.title = element_blank(),
        strip.text = element_blank(),
        panel.border = element_rect(color = "black", fill = NA, linewidth = 1.2)
    )

# Save the UMAP plot
ggsave(
    filename = output_file,
    plot = umap_plot_black,
    device = "png",
    width = 6,
    height = 6,
    dpi = 300
)

# Also print it to screen
print(umap_plot_black)
```

```{r}
# UMAP + clustering over all cells and catalogue
proj_10 <- UMAP_Harmony_clusters(proj_10)
```





```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj_10, colorBy = "cellColData",
    name = "Sample",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```




```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj_10, colorBy = "cellColData",
    name = "Clusters",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```
```{r}
subsetArchRProject(
    ArchRProj = proj_10,
    cells = getCellNames(proj_10),
    outputDirectory = "./tmp/ArchRProject_PBMCs_Combined_Beds_H3K27me3_Doublets_Removed_010126/",
    dropCells = TRUE,
    logFile = NULL,
    threads = getArchRThreads(),
    force = TRUE
)
```

```{r}
proj <- loadArchRProject(path = "./tmp/ArchRProject_PBMCs_Combined_Beds_H3K27me3_Doublets_Removed_010126/", force = FALSE, showLogo = TRUE)

getEmbedding(ArchRProj = proj, embedding = "UMAP_Harmony", returnDF = TRUE)
```



```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj, colorBy = "cellColData",
    name = "Clusters",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```

```{r}
proj <- addClusters(
    input = proj,
    method = "Seurat",
    name = "Clusters",
    reducedDims = "Harmony",
    resolution = 2,
    maxClusters = 25,
    verbose = FALSE,
    force = TRUE
)
```


```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj, colorBy = "cellColData",
    name = "Clusters",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```

```{r}
# Identify and remove high-doublet clusters (> 8.5%)
high_doublet_clusters <- c("C9", "C16") # , 'C99'
message("Removing clusters with >8.5% doublets: ", paste(high_doublet_clusters, collapse = ", "))

# Subset ArchRProject to exclude those clusters
proj <- proj[!(proj$Clusters %in% high_doublet_clusters), ]

# Optional: verify removal
table(proj$Clusters)
```
```{r}
# UMAP + clustering over all cells and catalogue
proj <- UMAP_Harmony_clusters(proj)
```



```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj, colorBy = "cellColData",
    name = "Clusters",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```


```{r}
# Identify and remove high-doublet clusters (> 8.5%)
high_doublet_clusters <- c("C90", "C91", "C96", "C2", "C66") # , 'C99'
message("Removing clusters with >8.5% doublets: ", paste(high_doublet_clusters, collapse = ", "))

# Subset ArchRProject to exclude those clusters
proj <- proj[!(proj$Clusters %in% high_doublet_clusters), ]

# Optional: verify removal
table(proj$Clusters)
```
```{r}
# UMAP + clustering over all cells and catalogue
proj <- UMAP_Harmony_clusters(proj)
```



```{r}
# Visualize clusters
plotEmbedding(
    ArchRProj = proj, colorBy = "cellColData",
    name = "Clusters",
    embedding = "UMAP_Harmony",
    size = 0.5,
    # pal= paletteContinuous(),
    plotAs = "points",
    # imputeWeights = getImputeWeights(proj),
    colorTitle = "mark"
) + theme_void() + theme(plot.title = element_blank()) #+ NoLegend()
```



```{r}
proj <- addGeneScoreMatrix(proj, force = TRUE) # , , useTSS = TRUE

proj <- addImputeWeights(proj)
```


```{r}
subsetArchRProject(
    ArchRProj = proj,
    cells = getCellNames(proj),
    outputDirectory = "./tmp/ArchRProject_PBMCs_Combined_Beds_H3K27me3_Doublets_Removed_021126/",
    dropCells = TRUE,
    logFile = NULL,
    threads = getArchRThreads(),
    force = TRUE
)
```
