---
title: "R Notebook"
output: html_notebook
---

## PBMC H3K4me3 H3K27me3 Cluster Analysis Files

### Input Files

- `./tmp/PBMCs_Combined_Beds_H3K4me3_Doublets_Removed_021126/`
- `./tmp/PBMCs_Combined_Beds_H3K27me3_Doublets_Removed_021126/`
- `../data/PBMC_WNN_cluster_assignments_021126.tsv`

### Output Files And Directories

- `./figures/paired_cells_umap_H23_vs_H12_n30_seed2.png`
- `./figures/H3K4_vs_H3K27_ECDF_plot.png`
- `./figures/H3K4_vs_H3K27_boxplot_pval.pdf`
- `./tmp/PBMC_Final_Marker_Gene_Analysis_012826/WNN_Clusters_040426/`
- `./tmp/PBMC_Final_Marker_Gene_Analysis_012826/WNN_Clusters_040426/H3K4me3_TCell_Naive_FDR_0.05_Log2FC_1.csv`
- `./tmp/PBMC_Final_Marker_Gene_Analysis_012826/WNN_Clusters_040426/H3K4me3_TCell_Reg_Exhausted_FDR_0.05_Log2FC_1.csv`
- `./tmp/PBMC_Final_Marker_Gene_Analysis_012826/WNN_Clusters_040426/H3K4me3_TCell_CM_FDR_0.05_Log2FC_1.csv`
- `./tmp/PBMC_Final_Marker_Gene_Analysis_012826/WNN_Clusters_040426/H3K4me3_TCell_4_FDR_0.05_Log2FC_1.csv`
- `./tmp/PBMC_Final_Marker_Gene_Analysis_012826/WNN_Clusters_040426/H3K4me3_BCell_1_FDR_0.05_Log2FC_1.csv`
- `./tmp/PBMC_Final_Marker_Gene_Analysis_012826/WNN_Clusters_040426/H3K4me3_BCell_2_FDR_0.05_Log2FC_1.csv`
- `./tmp/PBMC_Final_Marker_Gene_Analysis_012826/WNN_Clusters_040426/H3K4me3_Monocyte_FDR_0.05_Log2FC_1.csv`
- `./tmp/PBMC_Final_Marker_Gene_Analysis_012826/WNN_Clusters_040426/H3K4me3_NKCell_1_FDR_0.05_Log2FC_1.csv`
- `./tmp/PBMC_Final_Marker_Gene_Analysis_012826/WNN_Clusters_040426/H3K4me3_NKCell_2_FDR_0.05_Log2FC_1.csv`
- `./tmp/PBMC_Final_Marker_Gene_Analysis_012826/WNN_Clusters_040426/H3K4me3_Cytotoxic_FDR_0.05_Log2FC_1.csv`


```{r}
Sys.unsetenv("DISPLAY")

suppressPackageStartupMessages({
    library(ArchR)
    library(parallel)
    library(rtracklayer)
    library(repr)
    library(dplyr)
    library(plyr)
    library(Seurat)
    library(ggplot2)
    library(GenomicRanges)
    library(rtracklayer)

})
set.seed(1)

# Set default plot size
options(repr.plot.width=10, repr.plot.height=10)
```


```{r}
addArchRThreads(threads = 24)
addArchRGenome('hg38')
```



```{r}
proj <- loadArchRProject(path = "./tmp/ArchRProject/PBMCs_Combined_Beds_H3K4me3_Doublets_Removed_021126/", force = FALSE, showLogo = TRUE)

getEmbedding(ArchRProj = proj, embedding = "UMAP_Harmony", returnDF = TRUE)

```


```{r}
unique(proj$Sample)

```



```{r}
#Visualize clusters
plotEmbedding(ArchRProj = proj, colorBy = "cellColData", 
              name = "Clusters", 
              embedding = "UMAP_Harmony", 
              size =0.5, 
              #pal= paletteContinuous(), 
              plotAs= "points", 
              #imputeWeights = getImputeWeights(proj),
              colorTitle = 'mark'
             )+theme_void()+theme(plot.title = element_blank())#+ NoLegend()
```
```{r}
library(ggplot2)

# ------------------------------------------------------------
# Helper: sample N paired barcodes between two samples and plot
#   - all cells in light grey
#   - paired cells overlaid (bigger points)
#   - black line connecting each paired A/B cell
# ------------------------------------------------------------
plotPairedCellsOnUMAP <- function(
  proj,
  sample_A = "PBMC_CoCnT_K4me3_H23_010126",
  sample_B = "PBMC_CoCnT_K4me3_H12_010126",
  n_pairs  = 15,
  col_A    = "#1E90FF",
  col_B    = "#FF00FF",
  base_grey = "grey85",
  base_size = 0.3,
  overlay_size = 0.35,   # will be tripled below (so default behaves like before but 3x)
  seed = 2,
  embedding = "UMAP_Harmony"
) {

  # ---- pull UMAP and align to proj cellNames ----
  umap_mat <- proj@embeddings[[embedding]]$df
  umap_mat <- umap_mat[proj$cellNames, , drop = FALSE]

  meta <- as.data.frame(proj@cellColData)
  meta <- meta[proj$cellNames, , drop = FALSE]

  df <- meta
  df$UMAP_1 <- umap_mat[, 1]
  df$UMAP_2 <- umap_mat[, 2]
  df$cell   <- rownames(df)

  # ---- extract "suffix after #" for pairing ----
  df$barcode_suffix <- sub("^.*#", "", df$cell)

  # ---- subset the two samples ----
  if (!"Sample" %in% colnames(df)) {
    stop("proj@cellColData must contain a column named 'Sample'.")
  }

  dfA <- df[df$Sample == sample_A, , drop = FALSE]
  dfB <- df[df$Sample == sample_B, , drop = FALSE]

  # ---- find paired suffixes present in both ----
  common_suffix <- intersect(unique(dfA$barcode_suffix), unique(dfB$barcode_suffix))
  if (length(common_suffix) == 0) stop("No paired barcodes found between these samples.")

  # ---- choose how many pairs to plot ----
  set.seed(seed)
  n_pairs <- min(n_pairs, length(common_suffix))
  picked_suffix <- sample(common_suffix, n_pairs)

  # ---- pick one cell from each sample per suffix (in case duplicates exist) ----
  pick_one <- function(d, suffix_vec) {
    out <- lapply(suffix_vec, function(suf) {
      dd <- d[d$barcode_suffix == suf, , drop = FALSE]
      dd[sample(seq_len(nrow(dd)), 1), , drop = FALSE]
    })
    do.call(rbind, out)
  }

  overlayA <- pick_one(dfA, picked_suffix)
  overlayB <- pick_one(dfB, picked_suffix)

  # ---- build "segments" data for connecting lines ----
  overlayA$key <- overlayA$barcode_suffix
  overlayB$key <- overlayB$barcode_suffix

  seg_df <- merge(
    overlayA[, c("key", "UMAP_1", "UMAP_2")],
    overlayB[, c("key", "UMAP_1", "UMAP_2")],
    by = "key",
    suffixes = c("_A", "_B")
  )

  # ---- triple the overlay point size ----
  overlay_size <- overlay_size * 10

  # ---- plot: grey background, then black lines, then big colored points ----
  p <- ggplot(df, aes(UMAP_1, UMAP_2)) +
    geom_point(color = base_grey, size = base_size) +
    geom_segment(
      data = seg_df,
      aes(x = UMAP_1_A, y = UMAP_2_A, xend = UMAP_1_B, yend = UMAP_2_B),
      color = "black",
      linewidth = 1.5
    ) +
    geom_point(data = overlayA, aes(UMAP_1, UMAP_2), color = col_A, size = overlay_size) +
    geom_point(data = overlayB, aes(UMAP_1, UMAP_2), color = col_B, size = overlay_size) +
    theme_void() +
    theme(
      legend.position = "none",
      plot.margin = margin(5, 30, 5, 5)
    ) +
    ggtitle(paste0("Paired cells (n=", n_pairs, ")  ", sample_A, " vs ", sample_B))

  return(list(
    plot = p,
    picked_suffix = picked_suffix,
    segments = seg_df,
    overlayA = overlayA,
    overlayB = overlayB
  ))
}

```


```{r}
# -------------------------
# Example: start with 10
# -------------------------
# Run
res <- plotPairedCellsOnUMAP(
  proj,
  sample_A = "PBMC_CoCnT_K4me3_H23_010126",
  sample_B = "PBMC_CoCnT_K4me3_H12_010126",
  n_pairs = 10,
  seed = 20 #55 #60 #30 #20
)

# Save as PNG
ggsave(
  filename = "./figures/paired_cells_umap_H23_vs_H12_n30_seed2.png",
  plot = res$plot,
  width = 6,
  height = 8,
  dpi = 300
)

# Display
res$plot


```

```{r}
proj_K4me3 <- loadArchRProject(path = "./tmp/ArchRProject_PBMCs_Combined_Beds_H3K4me3_Doublets_Removed_021126/", force = FALSE, showLogo = TRUE)

getEmbedding(ArchRProj = proj_K4me3, embedding = "UMAP_Harmony", returnDF = TRUE)

```


```{r}
unique(proj_K4me3$Sample)

```

```{r}
## The original is ArchRProject_PBMCs_Combined_Beds_H3K27me3_Doublets_Removed_021126_V2
proj_K27me3 <- loadArchRProject(path = "./tmp/ArchRProject_PBMCs_Combined_Beds_H3K27me3_Doublets_Removed_021126/", force = FALSE, showLogo = TRUE)

getEmbedding(ArchRProj = proj_K27me3, embedding = "UMAP_Harmony", returnDF = TRUE)

```

```{r}
unique(proj_K27me3$Sample)

```

"PBMC_CoCnT_K27me3_H1_010126"
"PBMC_CoCnT_K27me3_H19_010126"

```{r}
# -------------------------
# Example: start with 10
# -------------------------
# Run
res <- plotPairedCellsOnUMAP(
  proj_K27me3,
  sample_A = "PBMC_CoCnT_K27me3_H1_010126",
  sample_B = "PBMC_CoCnT_K27me3_H19_010126",
  n_pairs = 10,
  seed = 1 #55 #60 #30 #20
)

# Save as PNG
ggsave(
  filename = "./figures/H3K27me3_paired_cells_umap_H1_vs_H19.png",
  plot = res$plot,
  width = 6,
  height = 8,
  dpi = 300
)

# Display
res$plot


```




```{r}
rd_obj <- proj@reducedDims[["Harmony"]]
class(rd_obj)
if (methods::is(rd_obj, "S4")) methods::slotNames(rd_obj)
str(rd_obj, max.level = 2)
head(rownames(get_rd_matrix(rd_obj)))
head(proj$cellNames)

```


```{r}
rd_obj <- proj@reducedDims[["Harmony"]]

class(rd_obj)
names(rd_obj)
sapply(rd_obj, class)

# show dimensions where possible
dims <- lapply(rd_obj, function(x) {
  if (is.matrix(x) || is.data.frame(x)) return(dim(x))
  if (inherits(x, "Matrix")) return(dim(x))
  return(NA)
})
dims

```

```{r}
get_rd_matrix <- function(rd_obj) {

  # If Harmony reduced dims are stored as a SimpleList (your case)
  if (inherits(rd_obj, "SimpleList")) {
    if ("matDR" %in% names(rd_obj)) {
      return(as.matrix(rd_obj[["matDR"]]))
    }
    stop("ReducedDims is a SimpleList but has no 'matDR' element. names(rd_obj): ", paste(names(rd_obj), collapse=", "))
  }

  # Already matrix / data.frame / sparse Matrix
  if (is.matrix(rd_obj)) return(rd_obj)
  if (is.data.frame(rd_obj)) return(as.matrix(rd_obj))
  if (inherits(rd_obj, "Matrix")) return(as.matrix(rd_obj))

  # Lists that store mat/df
  if (is.list(rd_obj)) {
    if (!is.null(rd_obj$mat)) return(as.matrix(rd_obj$mat))
    if (!is.null(rd_obj$df))  return(as.matrix(rd_obj$df))
  }

  # Generic S4 objects with slots
  if (methods::is(rd_obj, "S4")) {
    sn <- methods::slotNames(rd_obj)
    if ("mat" %in% sn) return(as.matrix(methods::slot(rd_obj, "mat")))
    if ("df"  %in% sn) return(as.matrix(methods::slot(rd_obj, "df")))
  }

  stop("Don't know how to extract a matrix from reduced_dim object of class: ",
       paste(class(rd_obj), collapse=", "))
}

```

```{r}
rd <- get_rd_matrix(proj@reducedDims[["Harmony"]])
dim(rd)         # should be 14851 x 15
head(rownames(rd))

```


```{r}
get_pairs_from_suffix <- function(df, sample_A, sample_B, sample_col = "Sample") {
  df$cell <- rownames(df)
  df$suffix <- sub("^.*#", "", df$cell)

  A <- df[df[[sample_col]] == sample_A, c("cell", "suffix"), drop = FALSE]
  B <- df[df[[sample_col]] == sample_B, c("cell", "suffix"), drop = FALSE]

  common <- intersect(unique(A$suffix), unique(B$suffix))
  if (length(common) == 0) stop("No shared suffixes found between sample_A and sample_B")

  A1 <- A[A$suffix %in% common, , drop = FALSE]
  B1 <- B[B$suffix %in% common, , drop = FALSE]
  A1 <- A1[!duplicated(A1$suffix), , drop = FALSE]
  B1 <- B1[!duplicated(B1$suffix), , drop = FALSE]

  merge(A1, B1, by = "suffix", suffixes = c("_A", "_B"))
}

pair_closeness_score <- function(
  proj,
  sample_A,
  sample_B,
  reduced_dim = "Harmony",
  dims_use = 1:15,         # Harmony has 15 dims in your object
  n_other = 5000,
  seed = 1,
  leq = TRUE,
  pool = c("union_samples", "all_cells")
) {
  pool <- match.arg(pool)

  # metadata aligned to proj$cellNames
  meta <- as.data.frame(proj@cellColData)
  meta <- meta[proj$cellNames, , drop = FALSE]
  if (!"Sample" %in% colnames(meta)) stop("Need meta column 'Sample' in proj@cellColData")

  # reduced dims matrix
  rd_obj <- proj@reducedDims[[reduced_dim]]
  if (is.null(rd_obj)) stop(paste0("proj@reducedDims[['", reduced_dim, "']] not found"))
  rd <- get_rd_matrix(rd_obj)

  # Align by shared cell names
  common_cells <- intersect(rownames(rd), rownames(meta))
  if (length(common_cells) < 10) stop("Too few shared cell names between reducedDims and metadata.")

  rd   <- rd[common_cells, , drop = FALSE]
  meta <- meta[common_cells, , drop = FALSE]

  dims_use <- dims_use[dims_use <= ncol(rd)]
  if (length(dims_use) < 2) stop("dims_use has <2 valid dims after checking reducedDims columns.")

  X <- rd[, dims_use, drop = FALSE]
  all_cells <- rownames(X)

  # pairs
  pairs <- get_pairs_from_suffix(meta, sample_A, sample_B, sample_col = "Sample")

  # pool for "other cells"
  pool_cells <- if (pool == "union_samples") {
    all_cells[meta$Sample %in% c(sample_A, sample_B)]
  } else {
    all_cells
  }
  pool_idx <- match(pool_cells, all_cells)
  pool_idx <- pool_idx[!is.na(pool_idx)]
  if (length(pool_idx) < 10) stop("Pool has too few cells. Check sample names.")

  # map pair cells to indices
  idx_A <- match(pairs$cell_A, all_cells)
  idx_B <- match(pairs$cell_B, all_cells)
  ok <- !(is.na(idx_A) | is.na(idx_B))
  pairs <- pairs[ok, , drop = FALSE]
  idx_A <- idx_A[ok]
  idx_B <- idx_B[ok]
  if (nrow(pairs) == 0) stop("No valid pairs after matching to reducedDims rownames.")

  if (!is.null(seed)) set.seed(seed)

  euclid_vec <- function(xi, M) {
    diffs <- M - matrix(xi, nrow = nrow(M), ncol = length(xi), byrow = TRUE)
    sqrt(rowSums(diffs^2))
  }

  s_for_cell <- function(i_idx, partner_idx) {
    xi <- X[i_idx, ]

    candidate <- pool_idx[pool_idx != i_idx & pool_idx != partner_idx]
    if (length(candidate) == 0) return(NA_real_)

    m <- min(n_other, length(candidate))
    others <- sample(candidate, m, replace = FALSE)

    d_pair <- sqrt(sum((xi - X[partner_idx, ])^2))
    d_others <- euclid_vec(xi, X[others, , drop = FALSE])

    if (leq) mean(d_others <= d_pair) else mean(d_others < d_pair)
  }

  s_A <- mapply(s_for_cell, idx_A, idx_B)
  s_B <- mapply(s_for_cell, idx_B, idx_A)

  out <- data.frame(
    suffix = pairs$suffix,
    cell_A = pairs$cell_A,
    cell_B = pairs$cell_B,
    s_A = as.numeric(s_A),
    s_B = as.numeric(s_B),
    stringsAsFactors = FALSE
  )
  out$S_pair <- rowMeans(out[, c("s_A", "s_B")], na.rm = TRUE)
  out
}

```

```{r}
# K4 project
scores_K4 <- pair_closeness_score(
  proj = proj_K4me3,  # <- your K4 ArchR project object
  sample_A = "PBMC_CoCnT_K4me3_H23_010126",
  sample_B = "PBMC_CoCnT_K4me3_H12_010126",
  reduced_dim = "Harmony",
  dims_use = 1:15,       # your Harmony has 15 dims
  n_other = 5000,
  seed = 1,
  leq = TRUE,
  pool = "union_samples"
)
scores_K4$assay <- "K4-K4"

# K27 project (edit sample names!)
scores_K27 <- pair_closeness_score(
  proj = proj_K27me3,  # <- your K27 ArchR project object
  sample_A = "PBMC_CoCnT_K27me3_H1_010126",  
  sample_B = "PBMC_CoCnT_K27me3_H19_010126",
  reduced_dim = "Harmony",
  dims_use = 1:15,
  n_other = 5000,
  seed = 1,
  leq = TRUE,
  pool = "union_samples"
)
scores_K27$assay <- "K27-K27"

```

  
  
```{r}
df_all$assay <- factor(df_all$assay, levels = c("K4-K4", "K27-K27"))

p_ecdf <- ggplot(df_all, aes(x = S_pair, color = assay)) +
  stat_ecdf(linewidth = 2) +
  coord_fixed(ratio = 1) +
  theme_classic() +
  theme(
    axis.line  = element_line(linewidth = 2),
    axis.ticks = element_line(linewidth = 2),
    axis.ticks.length = grid::unit(0.25, "cm"),
    axis.text  = element_text(size = 12),
    axis.title = element_text(size = 14),
    plot.title = element_text(size = 16),
    legend.position = c(0.68, 0.22),
    legend.background = element_rect(fill = scales::alpha("white", 0.7), color = NA),
    legend.key = element_rect(fill = NA, color = NA),
    legend.title = element_blank(),
    legend.text  = element_text(size = 11)
  ) +
  labs(
    x = "S_pair (fraction of sampled cells closer/equal than true partner; lower = better)",
    y = "ECDF",
    title = "Pair closeness in Harmony space: K4–K4 vs K27–K27"
  ) +
  scale_color_manual(values = c(
    "K4-K4"   = "#C93F2F",
    "K27-K27" = "#3F78A8"
  ))

print(p_ecdf)

ggsave(
  filename = "./figures/H3K4_vs_H3K27_ECDF_plot.png",
  plot = p_ecdf,
  width = 6,
  height = 6,
  dpi = 300
)
```
```{r}
p_box <- ggplot(df_all, aes(x = assay, y = S_pair, fill = assay)) +
  geom_boxplot(
    width = 0.75,
    outlier.shape = NA,
    linewidth = 0.8,
    color = "black"
  ) +
  scale_fill_manual(values = assay_cols) +
  theme_classic() +
  theme(
    axis.line  = element_line(linewidth = 2),
    axis.ticks = element_line(linewidth = 2),
    axis.ticks.length = grid::unit(0.25, "cm"),
    axis.text  = element_text(size = 12),
    axis.title = element_text(size = 14),
    plot.title = element_text(size = 16)
  ) +
  labs(
    x = NULL,
    y = "S_pair",
    title = "Pair closeness score (lower = better)"
  ) +
  ylim(0, 1) +
  annotate("text", x = 1.5, y = 0.95, label = pval_txt, size = 4)

# PDF (vector; no dpi needed)
ggsave(
  filename = "./figures/H3K4_vs_H3K27_boxplot_pval.pdf",
  plot = p_box,
  width = 3,
  height = 6,
  device = cairo_pdf
)

print(p_box)

```

```{r}
add_wnn_clusters <- function(proj, cluster_file) {
  # Extract pure barcodes from ArchR cell names
  barcodes <- sapply(strsplit(proj$cellNames, "#"), `[`, 2)
  proj$barcode <- barcodes

  # Read the cluster assignments from Python
  cluster_data <- read.table(
    cluster_file,
    header = TRUE,
    sep = "\t",
    stringsAsFactors = FALSE
  )

  # Keep only matching cells
  matched <- cluster_data[cluster_data$barcode %in% proj$barcode, ]
  matched <- matched[match(proj$barcode, matched$barcode), ]  # reorder

  # Add to ArchR project
  proj$WNN_Cluster <- matched$cluster

  # Subset project to only cells in the WNN set
  proj <- subsetCells(proj, cellNames = proj$cellNames[!is.na(proj$WNN_Cluster)])

  return(proj)
}

```

```{r}
proj <- add_wnn_clusters(
  proj,
  "./tmp/PBMC_WNN_cluster_assignments_021126.tsv"
)
```

"TCell_Naive":   '#016D4F',
    "TCell_Reg_Exhausted":   '#66C2A5',
    "TCell_CM":   '#A6D854',
    "BCell_1":   "#56B4E9",
    "BCell_2":   "#1F78B4",
    "Monocyte":  "#CC79A7",
    "NKCell_1":  "#F0C300",
    "NKCell_2":  "#E69F00",
    #"NKCell_3":  "#D55E00",
    "Cytotoxic":   "#984EA3"


```{r}
wnn_colors <- c(
  "TCell_Naive" = "#016D4F",
  "TCell_Reg_Exhausted" = "#66C2A5",
  "TCell_CM" = "#A6D854",
  #"TCell_4" = "#009E73",
  "BCell_1" = "#56B4E9",
  "BCell_2" = "#1F78B4",
  "Monocyte" = "#CC79A7",
  "NKCell_1" = "#F0C300",
  "NKCell_2" = "#E69F00",
  #"NKCell_3" = "#D55E00",
  "Cytotoxic" = "#984EA3"
)

# Get UMAP matrix
umap_mat <- proj@embeddings$UMAP_Harmony$df

# Match UMAP rows to the filtered proj$cellNames
umap_mat <- umap_mat[proj$cellNames, , drop = FALSE]

# Now you can safely assign
umap_df <- as.data.frame(proj@cellColData)
umap_df$UMAP_1 <- umap_mat[, 1]
umap_df$UMAP_2 <- umap_mat[, 2]

# Set cluster factor (optional ordering)
umap_df$WNN_Cluster <- factor(umap_df$WNN_Cluster, levels = names(wnn_colors))

# Reorder for layered plotting
umap_df <- umap_df[order(umap_df$WNN_Cluster), ]

# Plot
ggplot(umap_df, aes(x = UMAP_1, y = UMAP_2, color = WNN_Cluster)) +
  geom_point(size = 0.2) +
  theme_void() +
  theme(
    legend.position = "right",
    legend.title = element_text(size = 10, face = "bold"),
    legend.text = element_text(size = 9),
    plot.margin = margin(5, 30, 5, 5)
  ) +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  scale_color_manual(
    name = "WNN Cluster",
    values = wnn_colors
  )

```
```{r}
# Get the total number of cells in the ArchR project
num_cells <- nCells(proj)

# Print the number of cells
cat("Number of cells in the ArchR project:", num_cells, "\n")

```

```{r}
proj <- addGeneScoreMatrix(proj, force = TRUE) #useTSS = FALSE, 

proj <- addImputeWeights(proj)
```


```{r}
#proj$

markersGS <- getMarkerFeatures(
    ArchRProj = proj, 
    useMatrix = "GeneScoreMatrix", 
    groupBy = "WNN_Cluster",
    bias = c("TSSEnrichment","log10(nFrags)"),
   testMethod = "wilcoxon",
   #maxCells = 500,
   #scaleTo = 10^4,
   #threads = getArchRThreads(),
   #k = 100, 
   #bufferRatio = 0.8,
   #verbose = TRUE,
  #logFile = createLogFile("getMarkerFeatures")
)
```

"" = "#016D4F",
  "" = "#66C2A5",
  "" = "#A6D854",
  "" = "#56B4E9",
  "BCell_2" = "#1F78B4",
  "Monocyte" = "#CC79A7",
  "NKCell_1" = "#F0C300",
  "NKCell_2" = "#E69F00",
  "Cytotoxic" = "#984EA3"


```{r}

dir.create("./tmp/PBMC_Final_Marker_Gene_Analysis_012826/WNN_Clusters_040426/", recursive = TRUE, showWarnings = FALSE)

markerList <- getMarkers(markersGS, cutOff = "FDR <= 0.05 & Log2FC >= 1.0")
write.csv(markerList$TCell_Naive, file = "./tmp/PBMC_Final_Marker_Gene_Analysis_012826/WNN_Clusters_040426/H3K4me3_TCell_Naive_FDR_0.05_Log2FC_1.csv", row.names = FALSE)

markerList <- getMarkers(markersGS, cutOff = "FDR <= 0.05 & Log2FC >= 1.0")
write.csv(markerList$TCell_Reg_Exhausted, file = "./tmp/PBMC_Final_Marker_Gene_Analysis_012826/WNN_Clusters_040426/H3K4me3_TCell_Reg_Exhausted_FDR_0.05_Log2FC_1.csv", row.names = FALSE)

markerList <- getMarkers(markersGS, cutOff = "FDR <= 0.05 & Log2FC >= 1.0")
write.csv(markerList$TCell_CM, file = "./tmp/PBMC_Final_Marker_Gene_Analysis_012826/WNN_Clusters_040426/H3K4me3_TCell_CM_FDR_0.05_Log2FC_1.csv", row.names = FALSE)

markerList <- getMarkers(markersGS, cutOff = "FDR <= 0.05 & Log2FC >= 1.0")
write.csv(markerList$TCell_4, file = "./tmp/PBMC_Final_Marker_Gene_Analysis_012826/WNN_Clusters_040426/H3K4me3_TCell_4_FDR_0.05_Log2FC_1.csv", row.names = FALSE)

markerList <- getMarkers(markersGS, cutOff = "FDR <= 0.05 & Log2FC >= 1.0")
write.csv(markerList$BCell_1, file = "./tmp/PBMC_Final_Marker_Gene_Analysis_012826/WNN_Clusters_040426/H3K4me3_BCell_1_FDR_0.05_Log2FC_1.csv", row.names = FALSE)

markerList <- getMarkers(markersGS, cutOff = "FDR <= 0.05 & Log2FC >= 1.0")
write.csv(markerList$BCell_2, file = "./tmp/PBMC_Final_Marker_Gene_Analysis_012826/WNN_Clusters_040426/H3K4me3_BCell_2_FDR_0.05_Log2FC_1.csv", row.names = FALSE)

markerList <- getMarkers(markersGS, cutOff = "FDR <= 0.05 & Log2FC >= 1.0")
write.csv(markerList$Monocyte, file = "./tmp/PBMC_Final_Marker_Gene_Analysis_012826/WNN_Clusters_040426/H3K4me3_Monocyte_FDR_0.05_Log2FC_1.csv", row.names = FALSE)

markerList <- getMarkers(markersGS, cutOff = "FDR <= 0.05 & Log2FC >= 1.0")
write.csv(markerList$NKCell_1, file = "./tmp/PBMC_Final_Marker_Gene_Analysis_012826/WNN_Clusters_040426/H3K4me3_NKCell_1_FDR_0.05_Log2FC_1.csv", row.names = FALSE)

markerList <- getMarkers(markersGS, cutOff = "FDR <= 0.05 & Log2FC >= 1.0")
write.csv(markerList$NKCell_2, file = "./tmp/PBMC_Final_Marker_Gene_Analysis_012826/WNN_Clusters_040426/H3K4me3_NKCell_2_FDR_0.05_Log2FC_1.csv", row.names = FALSE)

markerList <- getMarkers(markersGS, cutOff = "FDR <= 0.05 & Log2FC >= 1.0")
write.csv(markerList$Cytotoxic, file = "./tmp/PBMC_Final_Marker_Gene_Analysis_012826/WNN_Clusters_040426/H3K4me3_Cytotoxic_FDR_0.05_Log2FC_1.csv", row.names = FALSE)

```
